|

### 2021-03-14 appendix/appendix.Rmd
add multilevel structure dataset

>>>>

[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.

[^freire]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

[^roman]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
